
https://www.yelp.com/biz/new-york-university-new-york-18

https://www.yelp.com/biz/columbia-university-new-york-43

Compare reviews to Twitter? Compare reviews of NYU vs. Columbia?

A tool to compare internet sentiment for NYU to any other university, create a comparison dashboard: vs. stars, reviews per user, sentiment on Twitter, etc. Data sources are Twitter and Yelp.

```{r}
library(tm)
library(twitteR)
library(stringr)
library(wordcloud)
library(syuzhet)
library(scales)
library(ggplot2)
library(tidyr)
library(dplyr)
```

Load initial Twitter authentification data.

```{r}
 #Load oauth keys
  api_key <- 	"fo13zkANmt0Jtr6iLfekHARRG"
  api_secret <- "	N1sLBOxbrvWKhocxQ88nMxuvz1ko1CsocfPLKFjMdfJFQjzCy2"
  token <- "801953993429778432-e47lzP8UGiTqPCl7yalcjQiXu2Ws0gI"
  token_secret <- "uLaIub69NFqqXuKYH6iC329W2q7hpVwSlcMQrQf9iEs2Z"
```

Create Twitter connection.

```{r}
setup_twitter_oauth(api_key, api_secret, token, token_secret)
```

First, for NYU.

```{r}
tweets.nyu <- searchTwitter("#nyu OR #NYU OR NYU OR nyu", n=100, lang="en")
tweets.columbia <- searchTwitter("#columbia OR #Columbia OR columbia OR Columbia", n=100, lang="en")
tweets.df.nyu <- twListToDF(tweets.nyu)
tweets.df.columbia <- twListToDF(tweets.columbia)
```

Remove @users.

```{r}
nohandles.nyu <- str_replace_all(tweets.df.nyu$text, "@\\w+", "")
nohandles.columbia <- str_replace_all(tweets.df.columbia, "@\\w+", "")
```

DF with most active users.

```{r}
tweets.df.nyu %>% group_by(screenName) %>% summarise(count = n()) %>% arrange(desc(count))
```


Create a corpus.

```{r}
wordCorpus <- VCorpus(VectorSource(nohandles.nyu))
```

Clean.

```{r}
wordCorpus <- tm_map(wordCorpus, removePunctuation)
wordCorpus <- tm_map(wordCorpus, content_transformer(tolower))
wordCorpus <- tm_map(wordCorpus, removeWords, stopwords("english"))
wordCorpus <- tm_map(wordCorpus, removeWords, c("amp", "2yo", "3yo", "4yo", "nyu"))
wordCorpus <- tm_map(wordCorpus, stripWhitespace)
```

Wordcloud.

```{r}
wordcloud(wordCorpus, scale=c(3.5, .35), max.words=50, random.order = F, colors = brewer.pal(6, "Dark2"))
```

Who's tweeting the most.

```{r}
handles <- str_extract_all(tweets.df.nyu$text, "@\\w+")
```

```{r}
handlesCorpus <- VCorpus(VectorSource(handles))
```

```{r}
wordcloud(handlesCorpus, scale=c(3,.3), max.words = 20, random.order = F, colors=brewer.pal(6, "Dark2"))
```

Sentiment analysis.

Use R base function iconv to remove non-ASCII characters.

```{r}
nyu.sentiment <- get_nrc_sentiment(iconv(tweets.df.nyu$text, "latin1", "ASCII", sub=""))
columbia.sentiment <- get_nrc_sentiment(iconv(tweets.df.columbia$text, "latin1", "ASCII", sub=""))
```

Add the sentiments to the NYU tweets dataframe.

```{r}
tweets.df.nyu <- cbind(tweets.df.nyu, nyu.sentiment)
tweets.df.columbia <- cbind(tweets.df.columbia, columbia.sentiment)
```

Plot.

```{r}
nyu.sentiment.sums <- data.frame(sentiment = colnames(nyu.sentiment),freq = colSums(nyu.sentiment))

columbia.sentiment.sums <- data.frame(sentiment = colnames(columbia.sentiment), freq = colSums(columbia.sentiment))
```

```{r}
#Combine them in a dataframe for comparison
review.comparison.df <- rbind(nyu.sentiment.sums, columbia.sentiment.sums)
nyu <- rep("nyu",10)
columbia <- rep("columbia",10)
schools <- c(nyu, columbia)
review.comparison.df$school <- schools
```

```{r}
plot <- ggplot(review.comparison.df, aes(x=sentiment, y=freq, fill=school)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_manual(values = c("#4F628E", "#9775AA")) + ggtitle("Twitter Sentiment Totals") + labs(x="Sentiment",y="Count") 
plot
```



